A Transformer Model for Retrosynthesis

### 2019-04-05 papers/retrosynthesis/article.tex
and

\author{
  Pavel Karpov\thanks{Helmholtz Zentrum M{\"u}nchen -- Research Center for Environmental Health (GmbH), Institute of Structural Biology, Ingolst{\"a}dter Landstra{\ss}e 1, D-85764 Neuherberg, Germany, \url{https://www.helmholtz-muenchen.de/stb/index.html}}\\
  Institute of Structural Biology\\
  Helmholtz Zentrum M{\"u}nchen\\
  BigChem GmbH \\
  Germany, Munich \\
  \texttt{carpovpv@gmail.com} \\
   \And 
  Guillaume Godin\\
  Firmenich International SA,\\
  Research\&Development Division, \\
  Switzerland, Geneva \\
  \texttt{guillaume.godin@firmenich.com}
  \And
  Igor V.~Tetko \\
  Institute of Structural Biology\\
  Helmholtz Zentrum M{\"u}nchen\\
  BigChem GmbH \\ 
  Germany, Munich \\ 
  \texttt{itetko@bigchem.de} \\
}

>>>>

\author{
  Pavel Karpov\thanks{Helmholtz Zentrum M{\"u}nchen -- Research Center for Environmental Health (GmbH), Institute of Structural Biology, Ingolst{\"a}dter Landstra{\ss}e 1, D-85764 Neuherberg, Germany, \url{https://www.helmholtz-muenchen.de/stb/index.html}}\\
  Institute of Structural Biology\\
  Helmholtz Zentrum M{\"u}nchen,\\
  and BigChem GmbH, \\
  Germany, Munich \\
  \texttt{carpovpv@gmail.com} \\
   \And 
  Guillaume Godin\\
  Firmenich International SA,\\
  Research\&Development Division, \\
  Switzerland, Geneva \\
  \texttt{guillaume.godin@firmenich.com}
  \And
  Igor V.~Tetko \\
  Institute of Structural Biology\\
  Helmholtz Zentrum M{\"u}nchen,\\
  and BigChem GmbH, \\ 
  Germany, Munich \\ 
  \texttt{itetko@bigchem.de} \\
}
